---
Title: P-Value
Author: Nima Niarad
Date: 6/25/2021
output: rmarkdown::github_document
---

<style> body {text-align: justify} </style> <!-- Justify text. -->

**P-Value Concept** 

Using Heart Disease UCI Data Set :https://www.kaggle.com/ronitf/heart-disease-uci  


```{r, echo=FALSE}

library(readr)
Heart <- read_csv("C:/Nima/Rstudio/Git/Data/Heart Disease UCI.csv")

```

**Simple Regression**

```{r, echo=FALSE}
lm.fit.1 = lm(age ~ chol + trestbps + fbs, data = Heart)
summary(lm.fit.1)

par(mfrow = c(2,2))
plot(lm.fit.1, pch = 20)
```

Normal Q-Q above indicating that quantiles come from a Normal Distribution as our data are almost on a line.

*chol* & *trestbps* have P-Values close to zero which means they are playing a key role in connection with age. Technically, it means they are statistically significant, **but Come OOOOn, what it meeeeans?!** 

If you are like that, we are on the same page. I hate those conceptual things that bring nothing but more complexity to the issue. Personally, I love simple examples, kinda story ones that give us the simple concept
behind the scene. So, let’s go for it with an example. I hope you find
it useful.

Imagine we have a friend named Jimmy. He goes to a specific bar with his friends every Friday night and they drink a lot! He goes to the bar other nights too, but occasionally.

The bar owner asks us to find out if **Jimmy** is playing a **key role** in increasing their **profit**!

When we are analyzing data, we make a distribution of revenue based on the number of drinks. We find out because of Jimmy, they make much more money on Friday nights. The bar owner tells us that he sometimes sees Jimmy on other nights too, so, would you tell me if having Jimmy on other nights is important or not?

When we look at our analysis, we came to an understanding that **Jimmy’s roles are not that important on other nights**. We are gonna say "Sir, there is a **slight chance** that you can **find Jimmy here at other nights**, but because of Friday nights, he is a real moneymaker!

So, Jimmy is playing a key role in the bar’s profit even if you consider other nights too! It is not by chance that Jimmy brings more money for the bar, despite the fact that we cannot see him on other nights. It means **P-Value for Jimmy would be close to zero for Friday nights** and he plays a key role in making more money for the bar.

We can make a Normal Distribution of Jimmy’s presence at the bar. Friday nights would be in the middle. When we do simple regression for Profit vs Jimmy on Friday nights, his P-value would be close to zero as it means this is not just a piece of luck that he increases the bar’s profit.

Is it a good example or what?!








 
