---
Title: PValues
Author: Nima Niarad
Date: 6/25/2021
output: rmarkdown::github_document
---

*P-Values Concept* 

Using Heart Disease UCI Data Set :https://www.kaggle.com/ronitf/heart-disease-uci  


```{r, echo=FALSE}
# P-Values Concept 

# Using Heart Disease UCI Data Set :https://www.kaggle.com/ronitf/heart-disease-uci 

library(readr)
Heart <- read_csv("C:/Nima/Rstudio/Git/Data/Heart Disease UCI.csv")

```

*Regression*

```{r}
lm.fit.1 = lm(age ~ chol + trestbps + fbs, data = Heart)
summary(lm.fit.1)
```


*chol* & *trestbps* have P-Values close to zero which means they are playing a key role in connection with age. Technically, it is said they are statistically significant.

The question is what it means exactly? 

Imagine you have a friend named Jimmy that goes to a specific bar every Friday night and drink a lot. He brings a lot of friends with himself too. He goes other night too, but you are not sure about it. The bar owner asks you to find out if Jimmy is playing a key role on increasing their profit on Friday nights much more than other busy nights there like Saturdays. When you collecting the data, you got a distribution of revenue based on the number of drinks. You find out because of Jimmy, they make much more money on Friday nights. The bar owner asks you he sometimes see Jimmy on other nights too, would you tell me if Jimmy can play a key role on other nights too? 
You are going to say to the owner that no, just Friday nights and Jimmy roles is not significant on other nights. 
What are you saying is there is slight chance that you can find Jimmy here at other nights, but he is here on Friday nights and making more money for you! So, Jimmy is playing a key role on the bar profit even if you consider other nights too. So, it is not by chance that Jimmy brings more money for the bar, however, we cannot find him in other nights. It means P-Values for Jimmy would be close to zero for other nights but he plays a key role on making more money for the bar.    








 
